Object Naming in Language and Vision: A Survey and a New Dataset

### 2020-03-12 papers/LREC2020/data-collection.tex
adds logos

\begin{figure}[htp]
	\centering
	\includegraphics[width=1\columnwidth]{figures/distr_imgs-per-domain_VG.png}
	\caption{Cumulative histograms of the number of images and names per domain in ManyNames.}
	\label{fig:overview_dataset1}
\end{figure}

@@

We then retrieved all VG images depicting an object whose name matches a word in these collection synsets or in those subsumed by them. We refer to the names obtained as \textit{seeds} ($450$~in total).
%\gbt{from the dataframe in the github it's 449. Also, there are some mistakes in the list of seeds ('dugout.', 'man's') -- to check after the deadline.}
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\word{pink bird}). 
We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.} 
% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
%\paragraph{Collection of instance candidates}
% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
% \paragraph{Sampling of instances}
Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$~instances for seeds with up to $800$~objects, and up to $1$K~instances for larger seeds. This yielded a dataset of $31,093$~instances, which was further pruned during annotation, as explained next.
Table~\ref{tab:overview_dataset1} shows the top $5$~\vg names in each of the domains. 
%\gbt{If someone feels like it: It'd be good to use small caps for domains throughout, and also to have the same (alphabetical?) order for all domains in all tables.}

>>>>

\begin{figure}[htp]
	\centering
	\includegraphics[width=1\columnwidth]{figures/distr_imgs-per-domain_VGMN.png}
	\caption{Cumulative histograms of the number of images and names per domain in ManyNames.}
	\label{fig:overview_dataset1}
\end{figure}

@@

We then retrieved all VG images depicting an object whose name matches a word in these collection synsets or in those subsumed by them. We refer to the names obtained as \textit{seeds} ($450$~in total).
%\gbt{from the dataframe in the github it's 449. Also, there are some mistakes in the list of seeds ('dugout.', 'man's') -- to check after the deadline.}
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\word{pink bird}). 
We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.} 
% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
%\paragraph{Collection of instance candidates}
% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
% \paragraph{Sampling of instances}
Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$~instances for seeds with up to $800$~objects, and up to $1$K~instances for larger seeds. This yielded a dataset of $31,093$~instances, which was further pruned during annotation, as explained next.
Figure~\ref{fig:overview_dataset1} shows the distribution of images and names in ManyNames per domain. 
%\gbt{If someone feels like it: It'd be good to use small caps for domains throughout, and also to have the same (alphabetical?) order for all domains in all tables.}
